### 2015-04-15 src/3_TimeSeries.tex
agregando tercera propuesta

A time series is a collection of observations in time (discrete or continuous).
The analysis of time series main objective is to find possible internal
structure in the data such as autocorrelation, trend or seasonal variation.
Some of application and uses of time series analysis are data compression,
explanatory variables (relationships with other variables, seasonal factors,
etc.), signal processing, forecasting (predict future values). This chapter
reviews the more relevant techniques in the rich and rapidly growing field of
time series analysis.

>>>>

A time series is a collection of observations in time (discrete or continuous).
The analysis of time series main objective is to find possible internal
structure in the data such as autocorrelation, trend or seasonal variation.
Some of application and uses of time series analysis are data compression,
explanatory variables (relationships with other variables, seasonal factors,
etc.), signal processing, forecasting (predict future values).  There are two
main approaches to study financial time series: to study directions of financial
rates and to explain financial rate volatility.  This chapter reviews the more
relevant techniques in the rich and rapidly growing field of time series
analysis considering these two approaches.

### 2015-04-15 src/4_OnlineLearning.tex
agregando tercera propuesta

Online learning is a supervised machine learning framework that is useful when we have sequential access to a sample only once.  This differs from the classical batch learning, where there is an entire data set available and the learner can build the internal model without any limits in accessing the data. In batch learning, there is time enough to carefully analyse the dataset, build large predictive models and combine them in a sophisticated way.

In only learning the goal is the same as batch learning, predicting targets as accurate as possible. For example, stock market prediction can be seen as online learning. The algorithm makes a prediction of the stock, little time after the real stock price is available, this information can be incorporated to the learner to further improve the prediction accuracy. In general, there is too much data available in an online learning setup, the data set grows continuously. Offline learning has equal or superior accuracy compared to online learning when the same amount of data is used.

@@

>>>>

Online learning is a supervised machine learning framework that is useful when
we have sequential access to a sample only once.  This differs from the
classical batch learning, where there is an entire data set available and the
learner can build the internal model without any limits in accessing the data.
In batch learning, there is time enough to carefully analyse the dataset, build
large predictive models and combine them in a sophisticated way. However, when
execution time is critical and new data is required to be included in the model,
online learning algorithms are a better option.

In batch learning, the training phase is commonly a computationally expensive
process. Therefore, when new data arrives it can't be included easily to the
model. Moreover, it could happen that we won't have enought time to process the
new data before more data arrives. In online learning algorithms there is no
training phase, but the model is updated and evaluated at every time step. This
model updating is computationally less expensive than a training phase.
Online algorithms allow incremental learning by processing one instance at a
time. This is done updating the current model instead of building the model from
scratch.

Online learning is also useful when some past data may be irrelevant
or we want to improve computational efficiency. However, the use of less
historical data could affect accuracy.

The goal of online learning is the same as batch learning, predicting targets as
accurate as possible. For example, stock market prediction can be seen as online
learning. The algorithm makes a prediction of the stock, little time after the
real stock price is available, this information can be incorporated to the
learner to further improve the prediction accuracy. In general, there is too
much data available in an online learning setup, the data set grows
continuously. Offline learning has equal or superior accuracy compared to online
learning when the same amount of data is used.

@@

There is sometimes confusion about online and incremental learning concepts.
Incremental learning refers to any online learning process that learns the same
model as would be learnt by a batch learning algorithm.

Incremental learning is useful when the input to a learning process is stream
data, with the need or desire to be able to use the result of learning at any
point in time, based on the input observations received so far.

In principle, the stream of observations may be infinitely long, or the next
observation long delayed, precluding any hope of waiting until all the
observations have been received. One would rather not simply accumulate and
store all the inputs and, upon receipt of each new one, apply a batch learning
algorithm to the entire sequence of inputs received so far. It would be
preferable compu- tationally if the existing hypothesis or other artifact of
learning could be updated in response to each newly received input observation.

Incremental learning is very useful when there is no need to record fundamental
data and only a summary needs to be retained. Due to this, incremental
algorithms are often characterized as memoryless, because no memory of past data
is required.  The algorithm is online but not incremental if it doesn't produce
the same result for all observations that the corresponding batch algorithm
would for these same observations.

Algorithm~\ref{alg:onlinealg} shows the online learning algorithm structure:

\begin{algorithm}[ht]
\begin{algorithmic}[1]
    \STATE Receives input $\mathbf{x}_t$
    \STATE Makes prediction $\mathbf{\hat{y}}_t$
    \STATE Receives response $\mathbf{y}_t$
    \STATE Incurs loss $l_t(\mathbf{y}_t,\mathbf{\hat{y}}_t)$
\end{algorithmic}
\caption{Structure of a Learning System}
\label{alg:onlinealg}
\end{algorithm}

\noindent where $l$ is some loss function. Performance is later measured after
$T$ trials as:

\begin{equation*}
L_T = \sum_{t=1}^T l_t(\mathbf{y}_t,\mathbf{\hat{y}}_t)
\end{equation*}

The objective is minimize this loss function for all instances.
The quality of online learning algorithms is measured by a quantity known as
regret which is the difference between the performance of the online algorithm
and its optimal predictor $E^* \in \Theta$ given by:

\begin{equation*}
L^*_T= \text{min}_{E \in \Theta} L_T^E \, ,
\end{equation*}

\noindent where $L_T^E = \sum_{t=1}^T
l_t(\mathbf{y}_t,\mathbf{y}^E_t)$ and $\mathbf{y}^E_t$ is the expert estimation.

Therefore regret is defined as:

\begin{equation*}
R_T = L_T - L^*_T
\end{equation*}
